Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-01-29 paper/compilation.tex
minor fixes.

  \caption{Example Product Graph IR construction for policy: $(\CD{W} \cdot \CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \Out) \Prefer (\CD{W} \cdot \CD{B} \cdot \In^* \cdot \Out)$.}
  \label{fig:example-compilation}
  \vspace{-1em}
\end{figure*}

@@

% Formally define automata
The RIR policy is an ordered sequence of regular expressions $r_1 \Prefer \dots \Prefer r_j$. While paths talk about the direction traffic flows through the network, to implement the policy with BGP we are concerned about the way control-plane information is disseminated (i.e., route announcements flowing in the opposite direction). To capture this idea, for each regular expression $r_i$, we construct a deterministic finite state machine on the reversed regular expression. Each automaton is a tuple: ($\Sigma, Q_i, F_i, q_{0_i}, \sigma_i$). The alphabet $\Sigma$ consists of all all abstraction locations (routers or ASes), $Q_i$ is the set of states for automaton i, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ is the state transition function.
%
% Formally define topology
The topology is represented as a graph ($V, E$), which consists of a set of vertices $V$, and a set of directed edges $E \colon 2^{V \times V}$.
%
% Formally define product graph
The combined PGIR is a tuple: ($V'$, $E'$, $s$, $e$, $P$) with
vertices $V' \colon V \times Q_1 \times \dots \times Q_j$,
edges $E' \colon 2^{V' \times V'}$,
a unique starting vertex $s$,
a unique ending vertex $e$,
and a preference function $P \colon V \rightarrow 2^{\set{1, \dots, j}}$ , which maps nodes in the product graph to a set of preference ranks.
For a vertex $v' = (v, \dots) \in V'$, we say $loc(v') = v$. 
A node $x$ shadows node $y$ in the product graph when $x \in V'$ and $y \in V'$ and $loc(x) = loc(y)$ but $x \neq y$. That is, $x$ shadows $y$ when they are different nodes in the PGIR that represent the same topology location.

@@

Intuitively, PGIR tracks which states of each automaton the policy is in as route announcements move between routers.
%
Consider the topology in Figure~\ref{fig:example-compilation}. Suppose we want a primary route from W that enters the network from $A$, and utilizes the A--C and C--D links. We also want a backup route that enters from $B$, and utilizes the B--C link, but is otherwise unconstrained. For simplicity, we assume that the route can end in either $X$, $Y$, or $Z$. The RIR for the policy is:
%
$$(\CD{W} \cdot \CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \Out) \Prefer (\CD{W} \cdot \CD{B} \cdot \In^* \cdot \Out)$$
%
Figure~\ref{fig:example-compilation} shows the policy automata for each regular expression preference. Since we are interested in the flow of control messages, the automata match backwards.
%
The figure also shows the PGIR after intersecting the topology and policy automata. Every path in it corresponds to a concrete path in the topology. In particular, every path through the PGIR that ends at a node $v$ such that the preference function $P(v) = \set{i_1, \dots, i_m}$ is non-empty, is a valid topological path that satisfies the policy constraints and results in a particular path with preferences $i_1$ through $i_m$.
%
For example, the path $X \cdot D \cdot C \cdot A \cdot W$ is a valid path in the topology that BGP route announcements might take, which would lead to obtaining the most prefered preference $1$.
BGP control messages can start from peer X, which would match the $\Out$ transition from both automata, leading to state $1$ in the first automaton, and state $1$ in the second automaton. This is reflected in the product graph by the node with state $(X,1,1)$. From here, if X were to advertise this route to D, it would result in the path $D X$, which would lead to state $2$ in the first automaton, and state $2$ in the second automaton, and so on.
%
The ``--" state indicates it is dropped from the corresponding automaton. Since node $(W,5,-)$ is in an accepting state for the first automata, it indicates this path has preference 1.

>>>>

  \caption{Example Product Graph IR construction for policy: $(\CD{W} \cdot \CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \Out) \Prefer (\CD{W} \cdot \CD{B} \cdot \In^+ \cdot \Out)$.}
  \label{fig:example-compilation}
  \vspace{-1em}
\end{figure*}

@@

% Formally define automata
The RIR policy is an ordered sequence of regular expressions $r_1 \Prefer \dots \Prefer r_j$. While paths talk about the direction traffic flows through the network, to implement the policy with BGP we are concerned about the way control-plane information is disseminated (i.e., route announcements flowing in the opposite direction). To capture this idea, for each regular expression $r_i$, we construct a deterministic finite state machine on the reversed regular expression. Each automaton is a tuple: ($\Sigma, Q_i, F_i, q_{0_i}, \sigma_i$). The alphabet $\Sigma$ consists of all all abstraction locations (routers or ASes), $Q_i$ is the set of states for automaton i, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ is the state transition function.
%
% Formally define topology
The topology is represented as a graph ($V, E$), which consists of a set of vertices $V$, and a set of directed edges $E \colon 2^{V \times V}$.
%
% Formally define product graph
The combined PGIR is a tuple: ($V'$, $E'$, $s$, $e$, $P$) with
vertices $V' \colon V \times Q_1 \times \dots \times Q_j$,
edges $E' \colon 2^{V' \times V'}$,
a unique starting vertex $s$,
a unique ending vertex $e$,
and a preference function $P \colon V \rightarrow 2^{\set{1, \dots, j}}$ , which maps nodes in the product graph to a set of preference ranks.
For a vertex $v' = (v, \dots) \in V'$, we say $loc(v') = v$. 
Two nodes $x$ and $y$ \emph{shadow} each other in the product graph when $x \in V'$ and $y \in V'$ and $loc(x) = loc(y)$ but $x \neq y$. That is, $x$ and $y$ shadow each other when they are different nodes in the PGIR that represent the same topology location.

@@

Intuitively, PGIR tracks which states of each automaton the policy is in as route announcements move between routers.
%
Consider the topology in Figure~\ref{fig:example-compilation}. Suppose we want a primary route from W that enters the network from $A$, and utilizes the A--C and C--D links. We also want a backup route that enters from $B$, and utilizes the B--C link, but is otherwise unconstrained. For simplicity, we assume that the route can end in either $X$, $Y$, or $Z$. The RIR for the policy is:
%
$$(\CD{W} \cdot \CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \Out) \Prefer (\CD{W} \cdot \CD{B} \cdot \In^+ \cdot \Out)$$
%
Figure~\ref{fig:example-compilation} shows the policy automata for each regular expression preference. Since we are interested in the flow of control messages, the automata match backwards.
%
The figure also shows the PGIR after intersecting the topology and policy automata. Every path in it corresponds to a concrete path in the topology. In particular, every path through the PGIR that ends at a node $v$ such that the preference function $P(v) = \set{i_1, \dots, i_m}$ is non-empty, is a valid topological path that satisfies the policy constraints and results in a particular path with preferences $i_1$ through $i_m$.
%
For example, the path $X \cdot D \cdot C \cdot A \cdot W$ is a valid path in the topology that BGP route announcements might take, which would lead to obtaining the most prefered preference $1$.
BGP control messages can start from peer X, which would match the $\Out$ transition from both automata, leading to state $1$ in the first automaton, and state $1$ in the second automaton. This is reflected in the product graph by the node with state $(X,1,1)$. From here, if X were to advertise this route to D, it would result in the path $D X$, which would lead to state $2$ in the first automaton, and state $2$ in the second automaton, and so on.
%
The ``--" state indicates the corresponding automaton can not accept the current path or any extension of it. Since node $(W,5,-)$ is in an accepting state for the first automata, it indicates this path has preference 1.
